Source Summaries

### 2020-02-17 paper/sourceSummaries/summary3.tex

\pagebreak

>>>>

\subsection{Bluetooth Low Energy Mesh Networks: A Survey}

\noindent
Jacob Ruud

\Urlmuskip=0mu plus 1mu\relax
\bibentry{seyedgomez2017}

\noindent
The authors analyze the composition, architecture, and implementation of Bluetooth Low Energy mesh networks. Their main goal with this paper is to assess the strengths and weaknesses of mesh networks as they compare to star networks that are beginning to phase out as the industry standard.

\noindent

In the open issues section of the paper, the authors use game theory to describe different scenarios that an attacker may be able to compromise a BLE mesh network.

\noindent
The majority of the work done for this paper was survery of proposed technologies, therefore the methods that the authors used for their conclusions involved reading publishings from other academics, corporations, and organizations and analyzing the architecture the each proposed. They used Bluetooth standards 4.0,4.1,4.2, and 5.0 in their comparison.

\noindent
The main security takaway from this paper is that bluetooth low enerygy was originally designed for a star topology, and therefore there exist a number of flaws in the implementation of mesh networks that still have yet to be sorted out. For example, currently data channels are protected by per-hop security; therfore, end-to-end encryption and authentication are not currently supported in BLE mesh networks. Also, routing and data packets that are transmitted through advertising channels are not secured unless the application layer provides a security solution.

\noindent
The authors suggested that future community work should focus on solving problems in security, multicast, and interoperability. They noted that these areas would best help deliver secure and high quality BLE mesh networks.

\Urlmuskip=0mu plus 1mu\relax
\pagebreak
